---
title: "ProductAssociatons"
author: "Stacey Jackson"
date: "03/04/2019"
output: word_document
---
```{r}
library(arules)
library(arulesViz)
library(dplyr)
```
####1. Upload the dataset

```{r}
transactions_B2C<-read.transactions(file="/Users/staceyjackson/Dropbox (Personal)/Ubiqum/DataAnalytics2/ProductAssociations/Data/B2CTransacs.csv",sep = ",", header = T, rm.duplicates = FALSE, quote = "\"'", skip = 0, encoding = "unknown")

summary(transactions_B2B)
str(transactions_B2B)

#transactions_B2B <- transactions %>% filter(V5=="B2B")


#transactions_B2B$V5 <- NULL
#transactions_B2B$V1<-NULL
#transactions_B2B$V4<-NULL



names(transactions_B2C)
str(transactions_B2C)
summary(transactions_B2C)
head(transactions_B2C)


```

```{r}

#orders_B2B <- as(B2BTransacs, "transactions")
#str(orders_B2B)

#v <- order_trans@itemInfo$labels
#v


#grep("Laptop",v)
#v[grep("Laptop",v)]<-"Laptop"
#print(v)

#order_trans@itemInfo$categories<-v
#str(order_trans)

```
####2. Inspect dataset
```{r}
length(transactions_B2C)
size(transactions_B2C)
LIST(transactions_B2C)
itemLabels(transactions_B2C)
```
####3. PLOTS OF FREQUENCY
####3.1 Plots of most frequent items
```{r}

itemFrequencyPlot(transactions_B2C,
                  type="relative",
                  topN=10,
                  horiz=TRUE,
                  col='steelblue3',
                  xlab='',
                  main='Item frequency, relative')

itemFrequencyPlot(transactions_B2C,
                  type="absolute",
                  topN=10,
                  horiz=TRUE,
                  col='steelblue3',
                  xlab='',
                  main='Item frequency, absolute')

itemFrequencyPlot(transactions_B2C,
                  type="relative",
                  topN=10,
                  horiz=FALSE,
                  col='steelblue3',
                  xlab='',
                  main='Item frequency, relative')

itemFrequencyPlot(transactions_B2C,
                  type="absolute",
                  topN=10,
                  horiz=FALSE,
                  col='steelblue3',
                  xlab='',
                  main='Item frequency, absolute')


```
####3.2 Plots of least frequent items
```{r}


barplot(sort(table(unlist(LIST(transactions_B2B))))[1:10]/9835,
        horiz=TRUE,
        las=1,
        col='steelblue3',
        xlab='',
        main='Frequency, relative')

barplot(sort(table(unlist(LIST(transactions_B2B))))[1:10],
        horiz=TRUE,
        las=1,
        col='steelblue3',
        xlab='',
        main='Frequency, absolute')
```
####3.3 Plot of a sammple
```{r}
image(sample(transactions_B2C,100))
image(sample(transactions_B2C,500))
```
####4. FIND ASSOCIATION RULES
####4.1 Without minlen

```{r}
rules <- apriori(transactions_B2C,parameter = list(supp=0.002, conf=0.2))
#rules.sorted <- sort(rules, by="lift")
inspect(rules)
summary(rules)


```
####4.2 With minlen
```{r}

rules <- apriori(transactions_B2B,parameter = list(minlen=2, supp=0.001, conf=0.1),control = list(verbose=F))
rules.sorted <- sort(rules, by="lift")
#inspect(rules.sorted)
ruleExplorer(rules.sorted)
```

####4.3 Inspect the rules
```{r}
inspect(head(rules.sorted,n=10))
labels(rules.sorted[1:10], itemSep = " + ", setStart = "", setEnd="", ruleSep = " ---> ")

```

####4.4 Plots of the rules
plot - The size of graph nodes is based on support levels and the colour on lift ratios. The incoming lines show the Antecedants or the LHS and the RHS is represented by names of items. 

```{r}
plot(rules.sorted)
plot(rules.sorted[1:10], method = "graph", control = list(type = "items"))
```
Another one
```{r}
plot(rules.sorted[1:10],method = "paracoord",control = list(reorder = TRUE))
```
Matrix of this
```{r}
plot(rules.sorted[1:10],method = "matrix")
```
scatterplot
```{r}
arulesViz::plotly_arules(rules.sorted)
```
####5.REDUNDANT RULES
```{r}
is.redundant(rules.sorted)
```
####5.1 Prune redundant rules
```{r}
subset.matrix <- is.subset(rules.sorted, rules.sorted)
subset.matrix[lower.tri(subset.matrix, diag=T)] <- NA
redundant <- colSums(subset.matrix, na.rm=T) >= 1
which(redundant)

rules.pruned <- rules.sorted[!redundant]
inspect(rules.pruned)
```
####6.SUBSET RULES
####6.1 iMac
```{r}
ItemRules_iMac<- subset(rules.sorted, subset=rhs %pin% "iMac")
ItemRules_iMac
inspect(ItemRules_iMac)
```
####6.2 Apple MacBook Air
```{r}

ItemRules_MacBook <- subset(rules.sorted, items %in% "Apple MacBook Air")
ItemRules_MacBook
inspect(ItemRules_MacBook)
```


