---
title: "ProductAssociatons"
author: "Stacey Jackson"
date: "03/04/2019"
output: word_document
---
```{r}
library(arules)
library(arulesViz)
library(dplyr)
```
####1. Upload the dataset

```{r}
transactions_B2B<-read.transactions(file="/Users/staceyjackson/Dropbox (Personal)/Ubiqum/DataAnalytics2/ProductAssociations/Data/B2BTransacs.csv",sep = ",", header = T, rm.duplicates = FALSE, quote = "\"'", skip = 0, encoding = "unknown")

transactions_B2C<-read.transactions(file="/Users/staceyjackson/Dropbox (Personal)/Ubiqum/DataAnalytics2/ProductAssociations/Data/B2CTransacs.csv",sep = ",", header = T, rm.duplicates = FALSE, quote = "\"'", skip = 0, encoding = "unknown")

Categories<-read.csv(file="/Users/staceyjackson/Dropbox (Personal)/Ubiqum/DataAnalytics2/ProductAssociations/Data/ProductCategories.csv", header=TRUE, sep=",")


```

####2. Inspect dataset
```{r}
length(transactions_B2B)
size(transactions_B2B)
#LIST(transactions_B2B)
itemLabels(transactions_B2B)
```
####3. PLOTS OF FREQUENCY
####3.1 Plots of most frequent items
```{r}

itemFrequencyPlot(transactions_B2B,
                  type="absolute",
                  topN=10,
                  horiz=FALSE,
                  col='steelblue3',
                  xlab='',
                  main='Item frequency, absolute')


```
####3.2 Plots of least frequent items
```{r}

barplot(sort(table(unlist(LIST(transactions_B2B))))[1:10],
        horiz=TRUE,
        las=1,
        col='steelblue3',
        xlab='',
        main='Frequency, absolute')
```
####4. ASSOCIATION RULES
```{r}

rules <- apriori(transactions_B2B,parameter = list(minlen=2, supp=0.002, conf=0.8),control = list(verbose=F))
rules.sorted <- sort(rules, by="lift")
inspect(rules.sorted[1:10])
#ruleExplorer(rules.sorted)
```

#### 5. CREATE LABELS FOR B2B CATEGORIES
```{r}
TempDFB2B <- as.data.frame(transactions_B2B@itemInfo$labels)

colnames(TempDFB2B) <- "ProdName"

TempDFB2B

TempDFB2B2 <- merge(TempDFB2B, Categories, by.x="ProdName", by.y="ProdName")

transactions_B2B@itemInfo$categories <- TempDFB2B2$BWCat

transactions_B2BAgg <- aggregate(transactions_B2B, by = "categories")

summary(transactions_B2BAgg)
str(transactions_B2BAgg)
```
####5.1.Plot for transactions_B2BAgg 
```{r}

itemFrequencyPlot(transactions_B2BAgg,
                  type="absolute",
                  topN=10,
                  horiz=FALSE,
                  col='steelblue3',
                  xlab='',
                  main='Item frequency, absolute')




```

#### 6. B2B TRANSACTION RULES
```{r}

rules <- apriori(transactions_B2BAgg,parameter = list(minlen=2, supp=0.002, conf=0.7),control = list(verbose=F))
rules.sorted <- sort(rules, by="lift")
inspect(rules.sorted[1:10])
labels(rules.sorted[1:10], itemSep = " + ", setStart = "", setEnd="", ruleSep = " ---> ")
#ruleExplorer(rules.sorted)
```

####6.1 Redundant rules
```{r}
is.redundant(rules.sorted)
which(is.redundant(rules.sorted), arr.ind = TRUE, useNames = TRUE)


```
####6.2 Prune redundant rules
```{r}

rules.sorted<- rules.sorted[!is.redundant(rules.sorted)]
is.redundant(rules.sorted)


```
####6.3 Inspect pruned rules
```{r}
#ruleExplorer(rules.pruned)
rules.pruned <- sort(rules, by="lift")
inspect(rules.pruned[1:10])
labels(rules.pruned[1:10], itemSep = " + ", setStart = "", setEnd="", ruleSep = " ---> ")

```
####6.4 Graph of the pruned rules
```{r}

plot(rules.pruned[1:10], method = "graph", control = list(type = "items"))
```
####7. CREATE LABELS FOR B2C CATEGORIES
```{r}
TempDFB2C <-
as.data.frame(transactions_B2C@itemInfo$labels)

colnames(TempDFB2C) <- "ProdName"

TempDFB2C

TempDFB2BC <-
 merge(TempDFB2C, Categories, by.x="ProdName", by.y="ProdName")



transactions_B2C@itemInfo$categories <- TempDFB2BC$BWCat

#creating transactional for Prod. Category
transactions_B2CAgg <- aggregate(transactions_B2C, by = "categories")

summary(transactions_B2CAgg)
str(transactions_B2CAgg)
```
####7.1 Plots of transactions_B2CAgg
```{r}

itemFrequencyPlot(transactions_B2CAgg,
                  type="absolute",
                  topN=10,
                  horiz=FALSE,
                  col='steelblue3',
                  xlab='',
                  main='Item frequency, absolute')




```
#### 8.B2C TRANSACTION RULES
```{r}

rulesB2C <- apriori(transactions_B2CAgg,parameter = list(minlen=2, supp=0.002, conf=0.7),control = list(verbose=F))
rulesB2C.sorted <- sort(rulesB2C, by="lift")
inspect(rulesB2C.sorted[1:10])
labels(rulesB2C.sorted[1:10], itemSep = " + ", setStart = "", setEnd="", ruleSep = " ---> ")
#ruleExplorer(rulesB2C.sorted)

```
####8.1 Redundant rules
```{r}
is.redundant(rulesB2C.sorted)
which(is.redundant(rulesB2C.sorted), arr.ind = TRUE, useNames = TRUE)

```
####8.2 Prune redundant rules
```{r}

rulesB2C.sorted<- rulesB2C.sorted[!is.redundant(rulesB2C.sorted)]
is.redundant(rulesB2C.sorted)

```
####8.3 Inspect pruned rules
```{r}
rulesB2C.pruned <- sort(rulesB2C.sorted, by="lift")
inspect(rulesB2C.pruned)
labels(rulesB2C.pruned, itemSep = " + ", setStart = "", setEnd="", ruleSep = " ---> ")

#ruleExplorer(rulesB2C.pruned)

```
####8.4 Graph of the pruned rules
```{r}

plot(rulesB2C.pruned, method = "graph", control = list(type = "items"))
```


